\chapter*{Acknowledgments}
\label{ch:ack}
I want to extend my sincere thanks to all those who accompanied me on my Research journey over the past two years. This period has been an amazing experience, brimming with priceless knowledge, personal development, and cherished memories.

Above all, I want to express my profound thanks and gratitude for Prof. Makarand Tapaswi. His support played a pivotal role in the realization of my ambitions, enabling me to reach heights I never thought possible. Thank you, for all your time and patience, for clearing all my trivial doubts and patiently listening to all I had to say. Not only in academics, but your guidance and personality have facilitated my personal growth.

Big shoutout to my amazing squad – Aditya, Amruth, Bhoomeendra, Dhaval, Prateek and Nayan! These awesome folks turned the academic rollercoaster into a joyride. From the \emph{special} late night lectures in felicity ground to sleepless research submissions, we did it all together. They aren't just friends; they're my academic family. We laughed through the highs and lows, celebrated victories, and turned stress into a comedy show. Thanks for being the sunshine in my research storm, and the reason my research journey is a tale worth telling. You guys are the real heroes of this academic saga!

Heartfelt gratitude to my rock-solid family -- Charchika, Mehul, Mom and Dad, you were my cheering squad, my emotional rescue team, and the reason I kept pushing forward. Your unwavering support and endless encouragement were the compass guiding me through uncharted research territories. Thank you for being my pillars of strength.
